\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Remove mention of active adversaries from Sec 6.1, per email thread.

\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions. Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version could use these inputs to profile users.

@@

We kept the user involved so that they explicitly start a connection to Tor. We chose not to leverage user inputs such as their location, risk, or other preferences due to active and passive adversaries. We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.

>>>>

%\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions. Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version could use these inputs to profile users.

@@

We kept the user involved so that they explicitly start a connection to Tor. We chose not to leverage user inputs such as their location, risk, or other preferences. We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.
